---
title: "AE-03: NYC flights — data wrangling"
author: "YOUR NAME HERE"
date: today
format:
  html:
    self-contained: true
    toc: true
    number-sections: false
    highlight-style: tango
    theme: cosmo
editor: visual
editor_options:
  chunk_output_type: console
---

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(nycflights13)
```

The `flights` data frame contains information about all flights departing from New York City (JFK, LGA, and EWR) in 2013. Each row represents one flight.

Before beginning, examine the data and its documentation:

```{r}
glimpse(flights)
?flights
```

# From MathLink cubes to flights

For each exercise:

1.  Before running your code, predict what the resulting rows and columns will represent.
2.  Write and run the pipeline.
3.  Check the output to determine whether the code did what you intended.

## Exercise 1: Filter using multiple conditions

Find flights that traveled to LAX **and** arrived on time or early.

Your result should have 10,059 rows and 19 columns.

```{r}

```

How did you check that every remaining flight satisfied both conditions?

> YOUR RESPONSE HERE

## Exercise 2: Combine verbs

Create a pipeline that:

- keeps flights traveling to LAX, BUR, or LGB;
- keeps only flights that departed early or arrived early;
- selects `year`, `month`, `day`, `origin`, `dest`, `dep_delay`, and `arr_delay`; and
- arranges the result from the largest to the smallest arrival delay.

Your result should have 12,492 rows and 7 columns.

```{r}

```

How did you check that your code worked as intended?

> YOUR RESPONSE HERE

## Exercise 3: Create new variables

Starting with `flights`, create:

- `hours`, which converts `air_time` from minutes to hours; and
- `mph`, which gives the flight's average speed using `distance` and `hours`.

Save the result as a new data frame named `flights_speed`. Then select `air_time`, `distance`, `hours`, and `mph` so you can inspect the calculation.

The first non-missing value of `mph` should be approximately 370.

```{r}

```

Why is it useful to inspect the original variables alongside the variables you created?

> YOUR RESPONSE HERE

## Exercise 4: Group and summarize

Create a variable named `on_time` that is `TRUE` when a flight departed on time or early and `FALSE` otherwise. Then calculate the proportion of on-time flights in each month.

Your result should have 12 rows. The proportion for January should be approximately 0.565.

```{r}

```

Explain how your code is working.

> YOUR RESPONSE HERE

# Your question

Write one question about these flights that can be answered by combining at least three `dplyr` verbs. Your pipeline must use at least one of `filter()`, `mutate()`, or `group_by()`.

**Question:**

> YOUR QUESTION HERE

Before running your code, describe what you expect the resulting data frame to represent. You do not need to predict its exact values or dimensions.

> YOUR PREDICTION HERE

```{r}

```

Describe one specific check you used to verify your result.

> YOUR RESPONSE HERE
