---
title: "AE 02: Exploring data through visualization"
author: "STAT 4380"
date: today
format:
  html:
    self-contained: true
    toc: true
    number-sections: false
    highlight-style: tango
    theme: cosmo
    df-print: paged
editor: visual
editor_options:
  chunk_output_type: console
---

## R Tips of the Day

1.  Take notes in this document! Will serve as a useful reference in Lab 02
2.  The "Save" Icon (+ Rendering)
3.  Code chunks
    - code goes on new line, NOT in curly brackets
    - Make sure "Play" button is visible
    - Source vs. Visual viewer
    - Suppressing messages, warnings, etc
    - echo
    - eval
4.  Installing packages
5.  Console versus .qmd

## Goals

Today, we will practice using visualization as a tool for **asking and refining questions**, not just answering questions we already have.

By the end of class, you should be able to:

- translate a question into a visualization;
- build and revise a `ggplot` in layers;
- describe what a visualization reveals and what it makes you wonder;
- make purposeful choices about plot type, aesthetics, and faceting.

You do not need to submit this application exercise. Follow along, experiment, and keep notes that will be useful for Lab 02.

## Packages

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(viridis)
```

## Meet the data

The `midwest` data frame is included in the **ggplot2** package. It contains demographic characteristics of counties in five Midwestern states.

```{r}
#| label: meet-data

glimpse(midwest)
```

Run `?midwest` in the Console to open the documentation.

### Before we plot

With a partner, take two minutes to inspect the variable names and documentation.

1.  What does each row represent?
2.  Which variables catch your attention?
3.  Write down **at least two questions** that these data might help us explore. Do not worry yet about how to code them.

> **Our question board:** Add one question from your pair to the class list.

## Cycle 1: Start simple, then notice

### Watch: one numerical variable

We will start with a broad question:

> How does population density vary across Midwestern counties?

As the plot develops, listen for the choices being made: What belongs on the x-axis? Which `geom` matches the variable type? Which decisions can change what we see?

```{r}
#| label: demo-pop-density

# Live code here
```

### Pause: notice and wonder

Individually, write down:

- one thing you **notice** in the plot;
- one thing you **wonder** because of the plot.

We will use a few of your observations to decide what to try next.

### Your turn

Explore the distribution of county poverty rates (`percbelowpoverty`).

1.  Create an appropriate visualization.
2.  Try at least two values for `bins` or `binwidth`. Which version helps you see the distribution more clearly?
3.  Give the plot an informative title and x-axis label.
4.  Be ready to share one thing you notice or wonder.

```{r}
#| label: your-turn-poverty

# Your code here

```

## Cycle 2: Build a relationship, then complicate it

### Watch: two numerical variables

> What is the relationship between the percentage of adults with a college degree (`percollege`) and the percentage of people below the poverty line (`percbelowpoverty`)?

Before we code: What plot type fits this question? What would you expect to see?

```{r}
#| label: demo-college-poverty

# Live code here
```

### What should we try next?

The first plot is rarely the final plot. What could explain variation or help us see the relationship more clearly?

We will choose one idea from the class and revise the plot.

```{r}
#| label: revise-college-poverty

# Revise the plot here

```

### Your turn (7 minutes)

Create a version of the college–poverty plot with a separate panel for each state.

- Add a smooth curve to each panel with `geom_smooth(se = FALSE)`.
- Include clear labels.
- Compare this plot with the original: What becomes easier to see? What becomes harder to see?

```{r}
#| label: your-turn-facets

# Your code here
```

> **Interpretation:**

## Cycle 3: Counts, proportions, and the question we mean to ask

The variable `inmetro` indicates whether a county is located in a metropolitan area. We will create a clearer categorical version.

```{r}
#| label: create-metro

midwest <- midwest |>
  mutate(metro = if_else(inmetro == 1, "Metro", "Non-metro"))
```

### Predict before plotting

Consider these two questions:

1.  Which states have the **largest numbers** of metro and non-metro counties?
2.  In which states is the **largest proportion** of counties metropolitan?

Would the same plot answer both questions? What would need to change?

### Watch: build the count version

```{r}
#| label: demo-metro-counts

# Live code here

```

### Your turn (5 minutes)

Modify the plot so each bar has the same total height and displays proportions rather than counts. Label the axes, legend, and plot.

```{r}
#| label: your-turn-metro-proportions

# Your code here

```

Discuss with your partner:

- Which question does each plot answer?
- What conclusion could someone get wrong if they used the count plot to compare proportions?

## Open exploration: follow a question

Return to our question board—or write a new question inspired by today’s plots. With your partner:

1.  State one question you want to investigate.
2.  Identify the variable or variables involved and their types.
3.  Choose a plot that fits the question.
4.  Create a first version.
5.  Look at it and revise **one thing** in response to what you see.
6.  Record one finding and one follow-up question.

You may use the [ggplot2 reference](https://ggplot2.tidyverse.org/reference/) or code from the lecture slides.

> **Question:**

```{r}
#| label: open-exploration

# Your code here
```

> **What we found:**

> **What we wonder next:**

## Wrap-up

Choose one prompt to discuss with your partner:

- What did you see someone do while coding today that you want to try again?
- When did a plot cause your question to change?
- What is one choice in a visualization that you now recognize as consequential?
