---
title: "AE-08 / Lab 6.5: Confidence Intervals and Hypothesis Tests"
subtitle: "due Thursday, October 31, 4:20pm"
author: "YOUR NAME HERE"
date: "`r Sys.Date()`"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
editor: visual
editor_options: 
  chunk_output_type: console
---

# Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE

# Packages

We'll use the `tidyverse` package for much of the data wrangling and visualization, and the data lives in the `openintro` package.

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(openintro)
library(broom)
```

## Data

We're going to revisit the `evals` data from last week. It comes from the `openintro` package.

```{r}
evals <- openintro::evals
```

# Exercises

Below is a model you fit last week, using `bty_avg` to predict `score`.

```{r}
m1 <- lm(score ~ bty_avg, data = evals)
tidy(m1)
```

## Analysis 1

A confidence interval for the slope, $\beta_1$ is computed by

$$b_1 \pm t_{1 - \alpha/2,n-2}SE(b_1)$$

1.  Which value in the output above gives $b_1$?

> YOUR ANSWER HERE (use inline code to extract)

2.  Which value in the output above gives $SE(b_1)$?

> YOUR ANSWER HERE (use inline code to extract)

3.  Assuming you want a 95% confidence interval, what is $1 - \alpha/2$?

> YOUR ANSWER HERE

4.  What is the value of $n$ for this data?

> YOUR ANSWER HERE (use inline code)

5.  Use the `qt()` function to find $t_{n-2}$ (assuming a 95% confidence interval)

```{r}

```

6.  Combine all of the above pieces to compute the confidence interval for $\beta_1$.

```{r}

```

7.  Interpret your interval.

> YOUR ANSWER HERE

8.  Use `confint()` to compute the same confidence interval.

```{r}

```

9.  Use `confint()` to compute a 99% confidence interval for $\beta_1$.

```{r}

```

## Analysis 2

We'll now consider a hypothesis test for whether there is a true relationship between `bty_avg` and `score`.

10. Write out appropriate null and alternative hypotheses using mathematical symbols.

$$typehere$$ $$typehere$$

The test statistic is given by $$T = \frac{b_1}{SE(b_1)}$$

11. Where can $T$ be found in the regression output? Use code to extract this value from the table, and verify that you get the same result by dividing the slope by its standard error.

```{r}

```

12. What critical value should the above test statistic be compared to? Assume an $\alpha = 0.05$ test.

> YOUR ANSWER HERE

13. Use the test statistic and critical value to draw a conclusion about the hypothesis test.

> YOUR ANSWER HERE

14. What is the p-value for this hypothesis test?

> YOUR ANSWER HERE (use inline code to extract)

15. Explain how this p-value relates to the test statistic.

> YOUR ANSWER HERE

16. Use the p-value to draw a conclusion about the hypothesis test.

> YOUR ANSWER HERE

17. Explain how you could have used your 95% confidence interval to draw a conclusion about this hypothesis test.

> YOUR ANSWER HERE

18. Create a scatterplot of the relationship described by this linear model, and include the line of best fit.

```{r}

```

19. Would you consider there to be a strong relationship between these two variables? Comment on how & why the results of the hypothesis test could be misleading. Is a confidence interval misleading in the same way? Why or why not?

> YOUR ANSWER HERE

# Submission & Grading

Unlike other AEs, this assignment will be graded for correctness, out of 20 points. Each exercise is worth 1 point, and the Reflection prompts are worth 1 point. You should submit your .html no later than class-time next Thursday.
