---
title: "Lab 03: College Majors"
author: "YOUR NAME HERE"
date: "`r Sys.Date()`"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
editor: visual
editor_options: 
  chunk_output_type: console
---

# Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE

```{r}
#| label: load-packages
#| message: false

```

# Exercise 1

# Exercise 2

```{r ex-2}
```

# Exercise 3

```{r ex-3}
```

# Exercise 4

```{r ex-4}
```

# Exercise 5

```{r ex-5}
```

# Exercise 6

```{r ex-6}
```

# Exercise 7

# Exercise 8

```{r ex-8}
```

# Exercise 9

```{r ex-9}

```

# Exercise 10

```{r ex-10}
```

# Exercise 11

```{r ex-11}
```

# Exercise 12

```{r ex-12}
```

# Exercise 13

# BONUS

```{r bonus}

```
